%        File: ans2012.tex
%     Created: Wednesday, January 25, 2012

\documentclass{anstrans}
%% To use the glossaries acronym package, you'll need to define any acronyms you intend to 
%% use. You can define acronyms with \newacronym{label}[acronym]{written out form}
%% To refer to them in the text use \gls{label}
\usepackage[acronym,toc]{glossaries}
\include{acros}
\makeglossaries


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{Thermal Calibration of an Analytical Repository Model using SINDA}
\author{Kathryn D.~Huff, Theodore H.~Bauer}

%% uncomment these next five only if using anstrans
\institute{Department of Nuclear Engineering \& Engineering Physics, University 
of Wisconsin, Madison, WI, 53706\\
Nuclear Engineering Division, Argonne National Laboratory, Argonne, IL, 60439}
\email{khuff@cae.wisc.edu \\
thbauer@anl.gov}
\usepackage{graphicx}
\usepackage{booktabs} % nice rules for tables
\usepackage{microtype} % if using PDF
\newcommand{\units}[1] {\:\text{#1}}%
\newcommand{\SN}{S$_N$}%{S$_\text{N}$}%{$S_N$}%


\date{January 27, 2012}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}

This work proposes a simple calibrated thermal resistance model to improve the 
accuracy of a rapid homogenous medium analytical transient heat transfer 
solution model. The model to be calibrated, created by \gls{LLNL}, is a solution 
of superimposed line and point source solutions representing a generic geologic 
repository with a gridlike waste package layout in a homogeneous medium. The 
auxillary thermal resistance model improves the model's estimation of the peak 
temperature and peak time. The calibration of this model is undertaken as part 
of a benchmarking effort against a geometrically detailed generic thermal 
repository model based on \gls{SINDAG} software.

Calibrated an analytic thermal repository model from (\gls{LLNL}) model using a 
thermal resistance model and determined appropriate coefficients from 
\gls{SINDAG} calculations. 


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Description of Work}

A benchmarking effort between the analytical \gls{LLNL} model and the 
\gls{SINDAG} \gls{ANL} model revealed a discrepancy between them. The time of 
peak heat arrived sooner and the value of the peak temperature was lower in the 
homogeneous medium \gls{LLNL} model than in the \gls{SINDAG} model. 

The SINDA model is based on a lumped parameter construction that models parts of 
the repository in detail. 

The LLNL model

Utilize coupled thermal models that separately address thermal behaviors at very 
different “length scales”.
Storage Unit Model: enclosed room, gallery, or tunnel that contains 
heat-generating waste packages.  Unit may be externally cooled or ventilated.
Host Rock Model: the repository’s surrounding host rock and its boundaries

Modeling Assumptions:
Host rock nodes are sized so that storage units account for only a small volume 
fraction
Temperature fields in storage units respond to changes in waste package decay 
heat much more rapidly than those in surrounding host rock. 

Solution Method
The transient host rock thermal model is solved directly on the basis of host 
rock material properties, boundary conditions, and the heat generated by any 
enclosed storage units. Generated heat is included through simple “point” or 
“line” sources within host rock nodes.  Temperature fields within each storage 
unit are determined by a steady-state solution of the storage unit model 
assuming its known heat generation rate and using the temperature in the 
surrounding host rock (as determined from the host rock model) as a nearby 
boundary condition. 

Calibration occured for geologies of interest.  


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results and Analysis}

The calibration was an improvement on the benchmarking.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions}

We recommend that for this and other analytical models of this nature, the 
additional step will improve results near the area of interest.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\nocite{<+ +>}
\bibliographystyle{ans}
\bibliography{ans2012}
\end{document}


